\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-05-31 graph_abs.tex
.

\begin{definition}[System Evolution]
    The behavior of system $\System$ at time $t$ is described as an
    evolution in the hybrid state-space $\HybridStates$ under the
    effect of the input $\vu \in \Inputs$ at time $t$. The forward
    simulation map $\simulate^\System : \HybridStates \times \Inputs
    \times \Reals^+ \mapsto \HybridStates$, maps a state $\x$ at time
    $t$ to a new state $\x'$ at time $t+\Delta_t$, under a constant
    input $\vu$.  Finally, we define the time and input parameterized
    reachability relation $\reach{t,u} \subseteq \HybridStates \times
    \HybridStates$ such that $(\vx,\vx') \in \reach{t,u}$ iff
    $\vx'=\simulate^{\System}(\vx,u,t)$.
\end{definition}

\mypara{System Assumptions:} We require that $\System$ can always be
simulated forward in time with deterministic results. This in turn
requires existence and uniqueness of trajectories over a finite time
horizon $[0,T]$, which can be guaranteed by Lipschitz continuity of
the vector field in each underlying hybrid mode, ruling away issues
such as finite escape times~\cite{Meiss/2007/Differential}, and having
well-defined semantics for simulations at switching boundaries. While
these assumptions hold for the dynamical system examples which we
consider in this paper, such assumptions can be restrictive for
general control system models. When analyzing a system that does not
obey theoretical conditions that allow deterministic simulation, we
assume that the underlying tool used for numerical approximations of
system behaviors uses deterministic simulation semantics.  Finally, we
assume full observability of the system state, validate our results
only against the $\simulate$ function (as the analytic closed-form
representation of the system dynamics is assumed to be unavailable).
From here on, we drop the subscript $\System$ whenever it is clear
from the context. Also, to ease the presentation, we conflate the
inputs with the state and denote them by $\vx$.

% Abstractions for black box systems
% graph based
% enrichment procedure

A discrete abstraction over a continuous space uses relations to
describe the behavior of the system over time. Such relations abstract
the underlying relation between concrete states, and concrete paths
can no longer be constructed directly. Instead, search procedures
like Counter-Example Guided Refinement must be used to find concrete
paths. In general, such search techniques are exponential with respect to
computational resources and memory. As an alternative, we introduce
data driven `enrichment' of abstractions to approximate the concrete
relations underlying the abstract relations. Informally, we use linear
regression to compute affine maps associated with the relations
between two abstract states. We then show how associating the computed
maps with the relations transforms a discrete abstraction into a PWA
transition system.

@@

>>>>

\begin{definition}[System Evolution]
    The behavior of system $\System$ at time $t$ is described as an
    evolution in the hybrid state-space $\HybridStates$ under the
    effect of the input $\vu \in \Inputs$ at time $t$. The forward
    simulation map $\mathsc{sim}^\System : \HybridStates \times \Inputs
    \times \Reals^+ \mapsto \HybridStates$, maps a state $\x\in\HybridStates$ at time
    $t$ to a new state $\x'\in\HybridStates$ at time $t+\Delta\in\Reals^+$, under a constant
    input $\vu$.  Finally, we define the time and input parameterized
    reachability relation $\reach{t,u} \subseteq \HybridStates \times
    \HybridStates$ such that
    \begin{equation}
        (\vx,\vx') \in \reach{t,u} \;\text{iff}\; \vx'=\mathsc{sim}^{\System}(\vx,u,t).
    \end{equation}
\end{definition}

\mypara{System Assumptions:} We require that $\System$ can always be
simulated forward in time with deterministic results. This in turn
requires existence and uniqueness of trajectories over a finite time
horizon $[0,T]$, which can be guaranteed by Lipschitz continuity of
the vector field in each underlying hybrid mode, ruling away issues
such as finite escape times~\cite{Meiss/2007/Differential}, and having
well-defined semantics for simulations at switching boundaries. While
these assumptions hold for the dynamical system examples which we
consider in this paper, such assumptions can be restrictive for
general control system models. When analyzing a system that does not
obey theoretical conditions that allow deterministic simulation, we
assume that the underlying tool used for numerical approximations of
system behaviors uses deterministic simulation semantics.  Finally, we
assume full observability of the system state, validate our results
only against the $\mathsc{sim}^\System$ function (as the analytic closed-form
representation of the system dynamics is assumed to be unavailable).
From here on, we drop the subscript $\System$ whenever it is clear
from the context. Also, to ease the presentation, we conflate the
inputs with the state and denote them by $\vx$.

@@

We base our methodology on the implicit discrete abstraction for
black-box dynamical systems~\cite{zutshi2014multiple}. The authors
showed how this abstraction is a graph abstraction, and reduced the
search for abstract violations to finding paths in a graph.

% Such an abstraction is defined by partitioning the
% state-space of the system using a grid, and hence each abstract state
% is a hyper-rectangle. The relations between abstract states are
% obtained by suitably lifting $(\vx,\vx') \in\reach{t,u}$. Considering
% the abstract states as vertices of a graph and the relations as edges
% between nodes, the problem of finding an abstract counter-example
% (CEx) can be cast as finding a path in the graph. Such an abstraction
% can be explored on-the-fly by enumerating the abstract relations
% between a pair of states.

\mypara{A discrete abstraction} over a continuous space uses relations
to describe the behavior of the system over time. Such relations
abstract the underlying relation between concrete states, and concrete
paths can no longer be constructed directly. Instead, search
procedures like Counter-Example Guided Refinement (CEGAR) must be used
to find concrete paths. In general, such search techniques are based
on refinement of the state-space and exponential with respect to
computational resources and memory. As an alternative, we introduce
data driven `enrichment' of abstractions to approximate the concrete
relations underlying the abstract relations.  Specifically, we use
linear regression to compute affine maps associated with the relations
between two abstract states. We then show how associating the computed
maps with the relations transforms a discrete abstraction into a PWA
transition system.

### 2017-05-31 prelims.tex
.

Temporal properties of pwa transitions systems can be checked using
off-the-shelf model checkers like SAL~\cite{SAL-SRI}, which can reason
over infinite state transitions systems using SMT solvers.
Furthermore, lazy SMT solvers can be employed for this specific
problem instance to achieve better efficiency~\cite{shoukry2017smc}.
We now show how relational pwa abstractions can be viewed as pwa
transition systems, and how the problem of falsification can
be answered by a BMC query.

>>>>

Temporal properties of PWA transitions systems can be checked using
off-the-shelf model checkers like SAL~\cite{SAL-SRI}, which can reason
over infinite state transitions systems using SMT solvers.
Furthermore, lazy SMT solvers can be employed for this specific
problem instance to achieve better efficiency~\cite{shoukry2017smc}.
We now show how relational PWA abstractions can be viewed as PWA
transition systems, and how the problem of falsification can
be answered by a BMC query.
